---
title: "Course 3, Task 2.3, Train The Models"
output: html_notebook
---

Load the caret library

```{r}
library(caret)
```

First, import and become familiar with the training set, "CompleteResponses.csv"

```{r}
CompleteResponses <- read.csv("CompleteResponses.csv", header=TRUE, sep=",")
```

Next, perform any necessary pre-processing

```{r}
#List the attributes within the data set

attributes(CompleteResponses)
```

```{r}
#Prints the min, max, mean, median, and quartiles of each attribute
summary(CompleteResponses)
```

There do not appear to be any missing values

```{r}
#Displays the structure of your data set
str(CompleteResponses)
```

```{r}
#Displays the attributes within your data set
names(CompleteResponses)
```

```{r}
#Will print out the instances within that particular column of your data set
CompleteResponses$elevel
```

```{r}
#histogram plot
hist(CompleteResponses$salary)
hist(CompleteResponses$age)
hist(CompleteResponses$elevel)
hist(CompleteResponses$car)
hist(CompleteResponses$zipcode)
hist(CompleteResponses$credit)
hist(CompleteResponses$brand)
```
1. There are more responses from 20-30 than any other age group
2. There are twice as many BMW owners that any other make of car
3. More of the responses favor Sony vs. Acer
4. Otherwise, the frequency for Salary, Education Level, and Zip Code is spread pretty evenly throughout the histogram groups

```{r}
#scatter (box) plot
plot(CompleteResponses$salary,CompleteResponses$brand)
plot(CompleteResponses$age,CompleteResponses$brand)
plot(CompleteResponses$elevel,CompleteResponses$brand)
plot(CompleteResponses$car,CompleteResponses$brand)
plot(CompleteResponses$zipcode,CompleteResponses$brand)
plot(CompleteResponses$credit,CompleteResponses$brand)
```
It appears that there may be a preference for Sony over Acer as the salary of the customer increases.

```{r}
#normal quintile plot to see if data is normally distributed
qqnorm(CompleteResponses$salary)
qqnorm(CompleteResponses$age)
qqnorm(CompleteResponses$elevel)
qqnorm(CompleteResponses$car)
qqnorm(CompleteResponses$zipcode)
qqnorm(CompleteResponses$credit)
qqnorm(CompleteResponses$brand)
```
The data appears to be normally distributed

Brand (of computer) will be the dependent variable

Now, create the training and test sets using createDataPartition
```{r}
#set the seed
set.seed(123)
```

