---
title: "A Short Introduction to the caret Package Tutorial"
output: html_notebook
---

The code in this notebook comes from "A Short Introduction to the caret Package
By Max Kuhn, August 6, 2015

install caret:

```{r}
install.packages("caret", dependencies = c("Depends", "Suggests"))
```

Had an error installing sjPlot, because of ggeffects not being available

Attempting installation using instructions from https://www.rdocumentation.org/packages/sjPlot/versions/2.8.12
```{r}
library(devtools)
devtools::install_github("strengejacke/sjPlot")
```
Also had an issue: ERROR: dependencies 'hardhat', 'modelenv' are not available for package 'workflows'
```{r}
install.packages("hardhat")
```

```{r}
install.packages("modelenv")
```

```{r}
install.packages("workflows")
```

ERROR: dependencies 'ggsci', 'ggsignif', 'rstatix' are not available for package 'ggpubr'
```{r}
install.packages("ggsci")
install.packages("ggsignif")
install.packages("rstatix")
install.packages("ggpubr")
```

ERROR: dependencies 'phylolm', 'phyr' are not available for package 'rr2'
```{r}
install.packages("pyholm")
install.packages("phyr")
install.packages("rr2")
```

ERROR: dependencies 'bigD', 'juicyjuice' are not available for package 'gt'
```{r}
install.packages("bigD")
install.packages("juicyjuice")
install.packages("gt")
```

ERROR: lazy loading failed for package 'trajectories'
```{r}
install.packages("intervals")
install.packages("trajectories")
```

Error: package or namespace load failed for 'svDialogs' in loadNamespace(i, c(lib.loc, .libPaths()), versionCheck = vI[[i]]):
 there is no package called 'svGUI'
 
```{r}
install.packages("svGUI")
install.packages("svDialogs")
```
ERROR: lazy loading failed for package 'cgam'
```{r}
install.packages("cgam")
```

